The Anatomy of a Hit: Statistically Learning from the Best

### 2024-04-22 paper/paper.qmd
started to organize paper, ran some models to test, etc.

---
title: "The Anatomy of a Hit: Statistically Learning from the Best"
subtitle: "Modeling the most impactful elements of the most popular musicians."
author: 
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/popularity-modeling."
date: April 18 2024
date-format: long
abstract: "We attempt to do some interesting things with models and music - stay tuned!"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
nocite: |
  @*
---

@@

@@

@@

@@

@@

## Weaknesses and next steps {#sec-weaknesses-next}

Weaknesses and next steps should also be included.

@@

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
# #| eval: true
# #| echo: false
# #| message: false
# #| warning: false
# #| label: fig-ppcheckandposteriorvsprior
# #| layout-ncol: 2
# #| fig-cap: "Examining how the model fits, and is affected by, the data"
# #| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
# 
# pp_check(first_model) +
#   theme_classic() +
#   theme(legend.position = "bottom")
# 
# posterior_vs_prior(first_model) +
#   theme_minimal() +
#   scale_color_brewer(palette = "Set1") +
#   theme(legend.position = "bottom") +
#   coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a hat plot. It shows... This suggests...

>>>>

---
title: "The Anatomy of a Hit: Statistically Learning from the Best"
subtitle: "An attempt to model"
author: 
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/popularity-modeling. Special thanks go to Rajan Maghera, Oliver Cao, and Hannah Yu for the support and encouragement. You're all wonderful."
date: April 18 2024
date-format: long
abstract: "We attempt to do some interesting things with models and music - stay tuned!"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
nocite: |
  @*
---

@@

## Workflow {#sec-first-point}
## Source
## Measurement and Sampling 
## Variables of Interest 
### Energy

```{r boilerplate-r-chunk}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: CAPTION
#| fig-align: ALIGNMENT

### Valence

```{r boilerplate-r-chunk}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: CAPTION
#| fig-align: ALIGNMENT

### Danceability

```{r boilerplate-r-chunk}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: CAPTION
#| fig-align: ALIGNMENT

### Explicit Status

```{r boilerplate-r-chunk}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: CAPTION
#| fig-align: ALIGNMENT

### Loudness

```{r boilerplate-r-chunk}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: CAPTION
#| fig-align: ALIGNMENT

### Duration

```{r boilerplate-r-chunk}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: CAPTION
#| fig-align: ALIGNMENT

@@

Create a Correl matrix to motivate choosing of variables.

@@

I guess put the results of the model?

@@

What does everything mean?

@@

## Weaknesses and next steps {#sec-weaknesses-next}
- Standard errors be huge. That means the regression is very imprecise. One way to
resolve that would be to get a larger sample size. 
- Sample size is kind of small - but that's the point? 
Maybe constructing a fuller dataset with the entire discographies 
of these people using Spotify's assistance would allow us to get more precise
estimates of effects. 
- People could repeat this experiment on a genre-based basis or using different 
ratings of artists. Perhaps there are genre-specific relationships within other 
variables in the spotify API that I haven't covered here.

::: {#refs}
:::

@@

# Model Testing

```{r boilerplate-r-chunk}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: CAPTION
#| fig-align: ALIGNMENT
